README

### 2017-04-13 src/README.Rmd
Correct Article_notes.csv; convert DOIs to lowercase in Rmd
DOI values now all converted to lowercase in RMD to join on

Still need to get complete file from office computer as the DOIs and
notes for this file in repository are incomplete currently

Then join the files together for complete reference and notes about
files
Import Bib file into R; update bibliography with missing refs and article notes csv file

```{r join_files}
articles <- read.csv("data/Journals_for_review.csv", strip.white = TRUE)

notes <- read.csv("data/Article_notes.csv", strip.white = TRUE)

>>>>

```{r join_files}
articles <- RefManageR::ReadBib("data/Journals_for_review.bib")
articles <- as.data.frame(articles)

notes <- read.csv("data/Article_notes.csv", strip.white = TRUE)
notes$DOI <- tolower(notes$DOI)
